Mitigating Interest Flooding DDoS Attacks in NDN

### 2013-01-12 01-intro.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

Various forms of distributed denial of services attack (DDoS) pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of addresses and making data the first-class network entities.
That is, instead of letting end hosts sending packets to a given IP address, NDN lets end hosts request desired data by sending Interest packets carrying application level data names.
Such a shift automatically eliminates several long standing DDoS attacks, including both direct flooding as well as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.

>>>>

Various forms of distributed denial of services (DDoS) attacks pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of addresses and making data the first-class network entities.
That is, instead of letting end hosts send packets to a given IP address, NDN lets end hosts request desired data by sending Interest packets carrying application level data names.
Such a shift automatically eliminates several long standing DDoS attacks, including both direct flooding as well as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.

### 2013-01-12 02-ndn-background.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

\section{NDN Overview\label{ccn-intro}}
%Named Data Networking (NDN) is a network architecture which aims to replace IP architecture by replacing IP’s host-to-host data delivery model with pull-based information retrieval model. In IP in order to retrieve data, data consumer have to know endpoint location of the desired data, in NDN all they have to know is data name. Names are hierarchical (non-flat) application-defined string names that are used for forwarding, routing and caching. A canonical NDN name looks in a following way: /ndn/ucla/CSdept/faculty/Lixia/webpage.

In this section we briefly introduce NDN with a focus on its stateful forwarding plane.
NDN is a receiver-driven, data-centric communication protocol.
All communication in NDN is performed using two distinct types of packets: \textit{Interest} and \textit{Data}. Both types of packets carry a \textit{name}, which uniquely identifies a piece of data that can be carried in one Data packet. Data names in NDN are hierarchically structured. A canonical NDN name looks in the following way: \texttt{\small /ndn/ucla/CS/www/index.html}.

To retrieve Data, a consumer puts the name of desired data into an Interest packet and sends it to the network.
Routers use this name to forward the Interest towards the data producer, and the Data packet whose name matches the name in the Interest is returned to the consumer.  All data packets carry a signature that binds the name to the data.
An Interest is “satisfied” when a Data packet is received with matching data name.

Each NDN node maintains three major data structures:
\begin{enumerate}
\item{Forwarding Interest Base (FIB) maps name prefixes and multiple physical network interfaces (where to forward Interests). Having one-to-many relationship in this table allows multipath forwarding of Interests.}
\item{Content Store (CS) temporarily buffers Data packets that pass through this node, allowing fast Data retrieval by different consumers.}
\item{Pending Interest Table (PIT) holds all ``not yet satisfied'' Interests that have been sent upstream towards data producers. Each entry in PIT contains a list of incoming, and outgoing, physical interfaces; the former enables multicast Data delivery, and the latter is needed when the same Interest is forwarded along multiple paths.}
\end{enumerate}

When a router receives an Interest packet, it first checks whether there is a matching Data in its Content Store.
If a match is found, the Data is sent back to the incoming interface of the Interest packet.
If not, the Interest name is checked against the entries in the PIT. 
If the name exists in the PIT already, then it can be either a duplicate Interest (i.e., its nonce is remembered in PIT entry) that should be dropped,
or an Interest from another consumer asking for the same Data which requires the incoming interface of this Interest to be added to the existing PIT entry.
If the name does not exist in the PIT, the Interest is added into the PIT and further forwarded to the interface chosen by the strategy module.

When a Data packet is received, its name is used to look up the PIT.
If a matching PIT entry is found,
the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the Content Store, and removes the PIT entry.  Otherwise, the Data packet is unsolicited and discarded. 
Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.

>>>>

\section{NDN Overview\label{ccn-intro}}
%Named Data Networking (NDN) is a network architecture which aims to replace IP architecture by replacing IPÕs host-to-host data delivery model with pull-based information retrieval model. In IP in order to retrieve data, data consumer have to know endpoint location of the desired data, in NDN all they have to know is data name. Names are hierarchical (non-flat) application-defined string names that are used for forwarding, routing and caching. A canonical NDN name looks in a following way: /ndn/ucla/CSdept/faculty/Lixia/webpage.

In this section we briefly introduce NDN with a focus on its stateful forwarding plane (for more details refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding}).
NDN is a receiver-driven, data-centric communication protocol.
All communication in NDN is performed using two distinct types of packets: \textit{Interest} and \textit{Data}. Both types of packets carry a \textit{name}, which uniquely identifies a piece of data that can be carried in one Data packet. Data names in NDN are hierarchically structured. A canonical NDN name looks in the following way: \ndnName{/ndn/ucla/CS/www/index.html}.

To retrieve Data, a consumer puts the name of the desired content into an Interest packet and sends it to the network.
Routers use this name to forward the Interest towards the Data producer, and the Data packet whose name matches the name in the Interest is returned to the consumer.  All Data packets carry a signature that binds the name to the Data.
An Interest is ``satisfied'' when a Data packet is received with matching data name.

Each NDN router maintains three major data structures:
\begin{itemize}
\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards data producers. Each entry in PIT contains a list of incoming, and outgoing, physical interfaces; the former enables multicast Data delivery, and the latter is needed when the same Interest is forwarded along multiple paths.
\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, defining allowed (multipath) directions where to forward Interests. 
% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing fast Data retrieval by different consumers.
\end{itemize}

When a router receives an Interest packet, it first checks whether there is a matching Data in its CS.
If a match is found, the Data is sent back to the incoming interface of the Interest packet.
If not, the Interest name is checked against the entries in the PIT. 
If the name exists in the PIT already, then it can be either a duplicate Interest (i.e., its nonce is remembered in PIT entry) that should be dropped,
or an Interest from another consumer asking for the same Data which requires the incoming interface of this Interest to be added to the existing PIT entry (``collapsing'' the Interests).
If the name does not exist in the PIT, the Interest is added into the PIT and further forwarded to the interface chosen by the strategy module, which uses FIB as input for its decision.

When a Data packet is received, its name is used to look up the PIT.
If a matching PIT entry is found,
the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.  Otherwise, the Data packet is unsolicited and discarded. 
Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
The lifetime is specified by users, but it is ultimately a router's decision for how long it is actually willing to keep the PIT entry.  
For example, and we assume this in the rest of the paper, the maximum time any Interest is kept in PIT is one second.

### 2013-01-12 03-interest-flooding.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers and are routed through the network based on their content name prefix. These properties make Interest packets an effective tool in launching DoS and DDoS attacks in NDN. An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}). We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.

@@

Since communication in NDN is content-centric, it is unlikely that an adversary can target specific routers or end-hosts, as neither is required to have a globally routable network identity/address. However, an adversary can target a specific namespace.
For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches. \footnote {In our example, Data producer is single-homed. In the case of multi-homed producers with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multi-path and adaptive forwarding~\cite{adaptive-forwarding}.} These large volume of Interests can distrupt service quality in NDN network in two ways: they \emph{create network congestion} and \emph{exhaust resources on routers}.

@@

To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., /newyorktimes/), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries (state) are stored at intermediate NDN routers for as long as possible.\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.  For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}
In order to achieve both requirements effectively, malicious Interests should avoid collapsing (i.e, request a content that is different than existing PIT entries in the network) and avoid being served from caches of intermediate routers (i.e., request unpopular or non-existing content). In other words, to maximize effect of an DDoS attack, each malicious Interest generated by an individual attacker bot should request a non-existing content with a unique name (\emph{unique junk Interests}). In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network. Other less effective strains of this attack can be mitigated by applying the same or similar countermeasures.

In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only i.e., we assume the routers in the network and the computers in the victim domain are not compromised.

>>>>

Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers, and are routed through the network based on their content name prefix. These properties make Interest packets an effective tool in launching DoS and DDoS attacks in NDN. An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}). We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.

@@

Since communication in NDN is content-centric, it is unlikely that an adversary can target specific routers or end-hosts, as neither is required to have a globally routable network identity/address. However, an adversary can target a specific namespace.
For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
\footnote {In our example, Data producer is single-homed. In the case of multi-homed producers with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding}.}
A large volume of these Interests can distrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.

@@

To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and avoid being served from caches of intermediate routers: each malicious Interest generated by an individual attacker bot should request an unpopular or non-existing content (e.g., content with a unique name, \emph{unique junk Interests}). In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network. Other less effective strains of this attack can be mitigated by applying the same or similar countermeasures.

In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.

### 2013-01-12 04a-design-naive.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
 fundamental principle of NDN architecture---flow balance between Interest and Data packets. The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet. This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests in the network. 
One simple implementation technique  is for a NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface. This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks. Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of Data requested that can fully utilize the downstream link (estimated from the number of Interests it forwarded) and once the link capacity limit has been reached, they no longer forward new incoming Interests. Ideally, the number of tokens {\it i.e.} the \emph{Pending Interests Limit} for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}. We can formalize this value as follows:
% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:

\begin{equation}
\mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
\end{equation}

>>>>

An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
 fundamental principle of NDN architecture---flow balance between Interest and Data packets. The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet. This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests in the network. 
One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface. This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks. Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of Data requested that can fully utilize the downstream link (estimated from the number of Interests it forwarded) and once the link capacity limit has been reached, they no longer forward new incoming Interests. Ideally, the number of tokens {\it i.e.} the pending \emph{Interests Limit} for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}. We can formalize this value as follows:
% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
%
\begin{equation}
\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
\end{equation}

### 2013-01-12 algos/dynamic-limits.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

The previous strategy -- the satisfaction-based Interest acceptance -- divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
An alternate strategy, which does not have the described drawbacks, is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.

>>>>

The previous strategy---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
An alternate strategy, which does not have the described drawbacks, is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.

### 2013-01-12 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@885 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@893 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

\title{Mitigating Interest Flooding DDoS Attacks in NDN}%:\\ Cache/Content Poisoning}
\author{anonymous}

\newfont{\nicettfont}{cmtt10}
\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
\renewcommand{\texttt}[1]{{\nicettfont #1}}
\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
\framebox{\begin{minipage}[c]{0.95 \columnwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algpseudocode,algorithm}
% More customizeable version. Probably it would be better to convert pseudocode to 2e format
% \usepackage{algorithm2e} 
\usepackage{multirow}

@@

\begin{abstract}
Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines. 
In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards data packets upon request only, effectively eliminating the existing DDoS attacks. 
However an NDN network can be subject to a new type of DoS attacks, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding.
We show that NDN's inherent properties of each router keeping per packet state and flow-balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
Our evaluation through simulations shows that the solution can quickly and effectively respond to Interest flooding.
\end{abstract}

@@

\bibliographystyle{IEEEtran}
\bibliography{references}

>>>>

\title{Mitigating Interest Flooding DDoS Attacks in NDN}%:\\ Cache/Content Poisoning}
\author{Anonymous}

\newfont{\nicettfont}{cmtt10}
\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
\renewcommand{\texttt}[1]{{\nicettfont #1}}

\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
\framebox{\begin{minipage}[c]{0.95 \columnwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algpseudocode,algorithm}
% More customizeable version. Probably it would be better to convert pseudocode to 2e format
% \usepackage{algorithm2e} 
\usepackage{multirow}
\usepackage{times}
\usepackage{color}

@@

\begin{abstract}
Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines. 
In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards data packets upon request only, effectively eliminating the existing DDoS attacks. 
However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding.
We show that NDN's inherent properties of each router keeping per packet state and flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
Our evaluation through simulations shows that the solution can quickly and effectively respond to Interest flooding.
\end{abstract}

@@

\bibliographystyle{IEEEtran}
{\small 
\bibliography{references}
}
